The fifteen year struggle of decentralizing privacy-enhancing technology

### 2014-03-26 paper.tex
The Onion Router was abbreviated as TOR, the current version is called Tor
Commented out paragraphs are bad, m'kay
would -> could

	The implementation of The Onion Router (Tor) was first described in 1996 by the U.S. Navy Research Laboratory, as a means to protect government communications from digital, as well as physical attacks, by hiding the location of the communicating party or parties \cite{goldschlag1996hiding}. The idea behind onion routing traces back to 1981, where Chaum described it in his famous paper "Untraceable electronic mail, return addresses, and digital pseudonyms" \cite{chaum1981untraceable}.

@@

	Decentralization is a difficult research problem. A trusted central authority simplifies bootstrapping, key management and user reputation. If one of these authorities were taken control of, anonymity would be compromised. When decentralizing a central authority, its functionality needs to be dispersed across the peers in the network. In this section we will explain the various problems involving Tor decentralization.

>>>>

	The implementation of The Onion Router (TOR) was first described in 1996 by the U.S. Navy Research Laboratory, as a means to protect government communications from digital, as well as physical attacks, by hiding the location of the communicating party or parties \cite{goldschlag1996hiding}. The idea behind onion routing traces back to 1981, where Chaum described it in his famous paper "Untraceable electronic mail, return addresses, and digital pseudonyms" \cite{chaum1981untraceable}.

@@

	Decentralization is a difficult research problem. A trusted central authority simplifies bootstrapping, key management and user reputation. If one of these authorities were taken control of, anonymity could be compromised. When decentralizing a central authority, its functionality needs to be dispersed across the peers in the network. In this section we will explain the various problems involving Tor decentralization.
